---
title: "Machine Learning in CDSS"
output: html_document
---

```{r include = FALSE}

```

This code is for BMI507-SP18 Class on Machine Learning for Classification and Clinical Decision Support.

We will use variables Smoker, age, Gender, height, weight, BMI, systolic and diastolic BP, and if you think any of the labs (d3) are important

## Create New Variables that are needed and merge into one dataframe!

# Dependent variable: diabetes diagnosis (ICD9 codes 250, 250.0, 250.*0 or #250.*2 (e.g., 250, 250.0, 250.00, 250.10, 250.52, etc)

# can use dmIndicator

```{r}

```


# Smoker or non-smoker severity level (SmokingStatus_Description)

```{r}

```



## fill in missing values using mean or median imputation

```{r}

```

## Split into Train, Validation, and Test set

```{r}

```

We will first run a logistic regression.


If target variable is factor, classification decision tree is built.
## Check if Outcome is a factor

```{r}

```

Now, let's compare using random forest. 

If target variable is factor, classification decision tree is built.
## Check if Outcome is a factor

```{r}

```

Finally, let's run the model as an SVM. 


```{r}

```
